Finite Time Bounds for Temporal Difference Learning with Function Approximation: Problems with some ``state-of-the-art'' results

### 2017-07-30 rebuttal.txt

We thank the reviewers for their comments.
Reviewer 1:
Naturally, we are disappointed by the negative recommendation, which we think is perhaps the result of overlooking some facts:
1) Two justifications for the iid setting: The noise is iid in the data-resampling setting, which is quite common in RL [4,10,15,16]. Understanding the differences between the standard supervised setting and the RL setting should start with a setting with the least number of differences. We see that already the iid noise setting presents surprises (see below)
2) Novelties are many:
i) Analysis of general LSA schemes with multiplicative noise for constant stepsize combined with PR averaging is new in literature. Prior results were known only for general LSA with additive noise and for SGD (a special case). New analysis required significant departure from the prior work and produces different results.
ii) Matrices in general LSA schemes lack symmetry, hence prior results do not apply directly; the similarity transformation that we employ in the paper is needed to handle the non-symmetric case; this is a major step
iii) We show a negative result: for general LSAs the stepsize cannot be chosen in a problem independent manner; we provide a lower bound to show that the negative result is not due to a weakness in our analysis
iv) Our results give better than previous rates for GTD. This way, our paper obviates a highly problematic projection step in GTD introduced by[10]; this is a major gain. The projection step is problematic because the range of dual variables cannot be known a priori in GTD.
We would like to mention that we have discussed the significance of our contributions in the introduction as well as section 6. Hence, we think that the negative position is unwarranted and lacks justification.

@@

Reviewer 2:
We will be happy to push the adaptive stepsize section to the appendix and provide a proof sketch in the main body.

Reviewer 3:
1) Missing citation to Prashanth, Korda and Munos' ECML'14 paper.
In fact, Prashanth and Korda later published arxiv.org/pdf/1411.3224.pdf (ICML'15), which we thought was the "state-of-the-art" and we cited this paper. Strangely, this paper does not cite the ECML'14 paper and so we failed to find the ECML'14 paper and hence failed to cite it. Now, as to the actual contributions, unfortunately, the ECML'14 paper seems to have many problems. In fact, a report by Lakshmi Narayanan and Szepesvári available at https://goo.gl/q9A4vn describes some of these problems. The factual errors are severe: for the expected error bound, on page 16 in Section A.2 of the arxiv version, after Eq. (26) it is claimed that \bar A_n - (1-beta) mu I is positive definite. This is easily seen to be false, e.g, when n = 1, in which case \bar A_n is rank 1, asymmetric and has nothing to do with mu, the minimum eigenvalue of the empirical feature covariance matrix. This is not a minor problem: Fixing the proof requires arguments similar to ours. The high-probability bound is similarly incorrect: On page 14, the display in the bottom of the page is just incorrect. Again, fixing the proof requires extra conditions, leading to an analysis similar to ours. As a sidenote, per the report above, it appears that the ICML'15 paper seems to have similar problems.

### 2017-07-30 issues.tex
no date
updated issues

\title{Finite Time Bounds for Temporal Difference Learning with Function Approximation: Bugs in state-of-the-art results}

@@

\author{
Chandrashekar Lakshmi Narayanan
\and
Csaba Szepesv\'ari 
%  David S.~Hippocampus\thanks{Use footnote for providing further
%    information about author (webpage, alternative
%    address)---\emph{not} for acknowledging funding agencies.} \\
%  Department of Computer Science\\
%  Cranberry-Lemon University\\
%  Pittsburgh, PA 15213 \\
%  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

which implies, e.g., that $\Psi=I$ (by choosing $\gamma=0$), which is not possible since the diagonal elements of $\Psi$ must some to one.

@@

>>>>

\title{Finite Time Bounds for Temporal Difference Learning with Function Approximation: Problems with some ``state-of-the-art'' results}

@@

\author{
Chandrashekar Lakshmi Narayanan
\and
Csaba Szepesv\'ari 
%  David S.~Hippocampus\thanks{Use footnote for providing further
%    information about author (webpage, alternative
%    address)---\emph{not} for acknowledging funding agencies.} \\
%  Department of Computer Science\\
%  Cranberry-Lemon University\\
%  Pittsburgh, PA 15213 \\
%  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}
\date{}

@@

which implies, e.g., that $\Psi=I$ (by choosing $\gamma=0$), which is not possible since the diagonal elements of $\Psi$ must sum to one.

@@

Also in page 14, we find the following inequality
\begin{align*}
(d+2)\left( e^{2(1+\beta)\sum_{k=1}^n \gamma_k}\norm{\theta_0}^2_2+ e^{2(1+\beta)\sum_{k=1}^n \gamma_k}\left(\sum_{k=1}^n \gamma_k e^{-(1+\beta)\sum_{j=1}^{k-1} \gamma_j}\right)^2+\norm{\theta^*}_2^2\right)\norm{\E(\epsilon_n|s_0)}_2\\
\leq (d+2)\frac{\norm{\theta_0}_2^2+1+\norm{\theta^*}_2^2}{(1-\beta)^2}e^{2(1+\beta)\sum_{k=1}^n \gamma_k}\norm{\E(\epsilon_n|s_0)}_2,
\end{align*}
where it is not clear as to how the $(1-\beta)^2$ factor appears in the denominator (also confirmed by a personal communication with one of the authors).
